---
title: "Enrichment Analysis"
author: Kristoforus 
date: 05/08/2019
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(biomaRt)
library(epitools)
library(stringr)
library(ensemblVEP)
library(MASS)
source("qqplot.R")

setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

# Setup mutation df
```{r}
df = read.csv("../exac_data/all_mutation_domain_specific.csv") # 2,667,962 rows (rows represents unique residue-mutation pairs)

# Extracting the sizes of every domain 
df$temp = paste(df$ENSP, df$residue, sep = "-") # creating temporary ENSP-residue column 
## for each residues, only keep the mutation with highest AF   
df = df[order(df$temp, -df$AF),]
df.uniq.pos = df[!duplicated(df$temp),] # 2,370,236 unique positions
result.uniq.pos = count(df.uniq.pos, ENSP, cluster_membership) # 36,208 unique domains
colnames(result.uniq.pos) <- c("ENSP", "cluster_membership", "cluster_size") 

# Extracting number of all mutations
df.uniq.pos.mutated <- df.uniq.pos[!is.na(df.uniq.pos$AF),] # 897,115 positions with mutation
result.all.var = count(df.uniq.pos.mutated, ENSP, cluster_membership)
colnames(result.all.var) <- c("ENSP", "cluster_membership", "n.mut.all") 

# Extracting number of all 4 possible combination of functional and common mutations 
## defining functional mutations as missense and nonsense mutations
functional <- unique(df.uniq.pos.mutated$mutation_type)[c(2,7,9,11,14,19,23,25,26)]
## rare functional 
df.rare.funcl <- df.uniq.pos.mutated[df.uniq.pos.mutated$mutation_type %in% functional 
                                         & df.uniq.pos.mutated$AF < 0.001,]
result.rare.funcl = count(df.rare.funcl, ENSP, cluster_membership)
colnames(result.rare.funcl) <- c("ENSP", "cluster_membership", "n.rare.funcl")
## common functional 
df.comm.funcl <- df.uniq.pos.mutated[df.uniq.pos.mutated$mutation_type %in% functional 
                                         & df.uniq.pos.mutated$AF > 0.001,]
result.comm.funcl = count(df.comm.funcl, ENSP, cluster_membership)
colnames(result.comm.funcl) <- c("ENSP", "cluster_membership", "n.comm.funcl")
## rare non-functional 
df.rare.nonfuncl <- df.uniq.pos.mutated[!(df.uniq.pos.mutated$mutation_type %in% functional) 
                                         & df.uniq.pos.mutated$AF < 0.001,]
result.rare.nonfuncl = count(df.rare.nonfuncl, ENSP, cluster_membership)
colnames(result.rare.nonfuncl) <- c("ENSP", "cluster_membership", "n.rare.nonfuncl")
## common non-functional 
df.comm.nonfuncl <- df.uniq.pos.mutated[!(df.uniq.pos.mutated$mutation_type %in% functional) 
                                         & df.uniq.pos.mutated$AF > 0.001,]
result.comm.nonfuncl = count(df.comm.nonfuncl, ENSP, cluster_membership)
colnames(result.comm.nonfuncl) <- c("ENSP", "cluster_membership", "n.comm.nonfuncl")


# Merging the data frames
domain.mutcount = merge(result.uniq.pos, result.all.var,by=c("ENSP", "cluster_membership"), all=TRUE)
domain.mutcount = merge(domain.mutcount,result.rare.funcl,by=c("ENSP", "cluster_membership"), all=TRUE)
domain.mutcount = merge(domain.mutcount,result.comm.funcl,by=c("ENSP", "cluster_membership"), all=TRUE)
domain.mutcount = merge(domain.mutcount,result.rare.nonfuncl,by=c("ENSP", "cluster_membership"), all=TRUE)
domain.mutcount = merge(domain.mutcount,result.comm.nonfuncl,by=c("ENSP", "cluster_membership"), all=TRUE)

domain.mutcount[domain.mutcount$n.mut.all %>% is.na(),]$n.mut.all <- 0 
domain.mutcount[domain.mutcount$n.rare.funcl %>% is.na(),]$n.rare.funcl <- 0 
domain.mutcount[domain.mutcount$n.comm.funcl %>% is.na(),]$n.comm.funcl <- 0
domain.mutcount[domain.mutcount$n.rare.nonfuncl %>% is.na(),]$n.rare.nonfuncl <- 0
domain.mutcount[domain.mutcount$n.comm.nonfuncl %>% is.na(),]$n.comm.nonfuncl <- 0

write.csv(domain.mutcount, "domain_level_mutation_counts.csv",row.names = FALSE) # 36,208 unique domains
```


# Analysis using Fisher's Test 
```{r}
# Extract number of protein-level size and mutations counts 
prot.lvl.mutcount = domain.mutcount %>% group_by(ENSP) %>% 
  summarise(prot.size=sum(cluster_size), n.mut.prot = sum(n.mut.all)) 
domain.mutcount = merge(domain.mutcount, prot.lvl.mutcount, by="ENSP", all=TRUE) 

# Defining Fisher's test function 
map.fisher <- function(row){
  in.mut <- row$n.mut.all 
  in.not <- row$cluster_size - in.mut 
  out.mut <- row$n.mut.prot - in.mut
  out.not <- (row$prot.size - row$cluster_size) - out.mut
  mtx = matrix(c(in.mut, in.not, out.mut, out.not), 2,2)
  
  fisher_or = fisher.test(mtx, alternative = "two.sided", conf.level = 0.9)$estimate
  fisher_p = fisher.test(mtx, alternative = "two.sided", conf.level = 0.9)$p.value
  fisher_midp = ormidp.test(in.mut, in.not, out.mut, out.not)[2] %>% as.numeric
  
  return(c(fisher_or, fisher_p, fisher_midp) %>% as.numeric())
}

# map fisher's exact test for every row of the domain-level mutation df
temp <- sapply(1:nrow(domain.mutcount), function(i){map.fisher(domain.mutcount[i,])})

temp %>% dim()
# add fisher's odd ratio and p-value into the domain-level mutation df
domain.mutcount$Fisher.odd.ratio <- temp[1,] 
domain.mutcount$Fisher.p.val <- temp[2,]
domain.mutcount$Fisher.mid.p <- temp[3,]

domain.mutcount
```

## Plotting p-value histogram and qqplots 
```{r}
# raw p-value
ggplot(domain.mutcount, aes(x=Fisher.p.val)) + geom_histogram()
qqunif.plot(domain.mutcount$Fisher.p.val + 1e-6)
# after mid-p adjustment 
ggplot(domain.mutcount, aes(x=Fisher.mid.p)) + geom_histogram()
qqunif.plot(domain.mutcount$Fisher.mid.p + 1e-6)
# after BH adjustement
domain.mutcount$Fisher.BH.adj <- p.adjust(domain.mutcount$Fisher.mid.p, "BH")
ggplot(domain.mutcount, aes(x=Fisher.BH.adj)) + geom_histogram()
qqunif.plot(domain.mutcount$Fisher.BH.adj + 1e-6)
```

## Retrieving significantly constrained domains
```{r}
# p-value cutoff of 0.1 here is because we used two tailed test to ensure mid-p value histogram has a uniform baseline before adjusting it using Benjamini Hochberg correction.  
constrained.Fisher = domain.mutcount[domain.mutcount$Fisher.BH.adj < 0.1 &
                                      domain.mutcount$Fisher.odd.ratio < 1,] 
# 1,123/36,028 of the domains are constrained (3.12%) 
# 974/6,946 of the proteins have at least one constrained domain(14.0%)
```


# RVIS analysis 
## Regress number of all mutation in a domain with number of rare mutations and calculate studentised residuals
```{r}
domain.mutcount
ggplot(domain.mutcount, aes(x=n.mut.all, y=n.rare.funcl)) + geom_point()
ggplot(domain.mutcount, aes(x=n.mut.all, y=n.comm.funcl)) + geom_point()
ggplot(domain.mutcount, aes(x=n.mut.all, y=n.rare.funcl+n.comm.funcl)) + geom_point()

domain.lm <- lm(n.comm.funcl ~ n.mut.all, domain.mutcount)
summary(domain.lm) # p.val = 2e-16, R-squared=0.337
rare.var <- lm(n.rare.funcl ~ n.mut.all, domain.mutcount)
summary(rare.var) # p.val = 2e-16, R-squared=0.9686 
all.funcl.var <- lm(n.comm.funcl + n.rare.funcl ~ n.mut.all, domain.mutcount)
summary(all.funcl.var) # p.val = 2e-16, R-squared=0.969 

domain.mutcount$RVIS.dom <- studres(domain.lm)
```

## Plot the distribution of domain-level RVIS scores
```{r}
ggplot(domain.mutcount, aes(RVIS.dom)) + geom_histogram()

# define the domains having the bottom 5% RVIS scores as constrained
constrained.dom.RVIS <- 
  domain.mutcount[order(domain.mutcount$RVIS.dom),][1:as.integer(0.05*nrow(domain.mutcount)),]
# 1,810/36,028 of the domains are constrained (5%, defined)
# 1,429/6,946 of the proteins have at least one constrained domain (20.5%)

constrained.dom.RVIS$constrained.dom <- TRUE
domain.mutcount <- merge(domain.mutcount, constrained.dom.RVIS[
  c("ENSP","cluster_membership","constrained.dom")],
  by=c("ENSP", "cluster_membership"),all=TRUE)
domain.mutcount[is.na(domain.mutcount$constrained.dom),]$constrained.dom <- FALSE

# Plotting regression again with colors
ggplot(domain.mutcount, aes(x=n.mut.all, y=n.comm.funcl, color=constrained.dom)) +
  geom_point() + 
  geom_smooth(color="black", method="lm", se=FALSE, linetype="solid", fullrange=TRUE) +
  scale_color_manual(values = c("grey", "red"))

# Now define it as bottom 1% instead
constrained.dom.RVIS2 <- # 99th percentile instead
  domain.mutcount[order(domain.mutcount$RVIS.dom),][1:as.integer(0.01*nrow(domain.mutcount)),]
# 362/36,028 of the domains are constrained (5%, defined)
# 358/6,946 of the proteins have at least one constrained domain (20.5%)

constrained.dom.RVIS2$constrained.dom2 <- TRUE
domain.mutcount <- merge(domain.mutcount, constrained.dom.RVIS2[
  c("ENSP","cluster_membership","constrained.dom2")],
  by=c("ENSP", "cluster_membership"),all=TRUE)
domain.mutcount[is.na(domain.mutcount$constrained.dom2),]$constrained.dom2 <- FALSE

lm(domain.mutcount$n.comm.funcl~domain.mutcount$n.mut.all) %>% summary
# Plotting regression again with colors
ggplot(domain.mutcount, aes(x=n.mut.all, y=n.comm.funcl)) + 
  geom_point(aes(colour = constrained.dom2)) +
  scale_color_manual(name = c(), values = c("grey", "red"), labels = c("unconstrained", "constrained")) + 
  geom_smooth(color="black", method="lm", se=FALSE, linetype="solid", fullrange=TRUE) +
  xlab("All ExAC mutations count") + 
  ylab("Common missense and nonsense count") + 
  ggtitle("RVIS Plot")

```

## Regress number of all mutation in a protein with number of rare mutations and calculate studentised residuals
```{r}
# Extract number of protein-level size and mutations counts 
prot.lvl.funcl.mutcount = domain.mutcount %>% group_by(ENSP) %>% 
  summarise(n.prot.comm.funcl = sum(n.comm.funcl), n.prot.rare.funcl = sum(n.rare.funcl)) 
domain.mutcount = merge(domain.mutcount, prot.lvl.funcl.mutcount, by="ENSP", all=TRUE) 

domain.mutcount %>% colnames()
prot.lvl.mutations <- domain.mutcount[,c("ENSP","prot.size","n.mut.prot",
                                         "n.prot.comm.funcl","n.prot.rare.funcl")] %>%
  unique 

ggplot(prot.lvl.mutations, aes(x=n.mut.prot, y=n.prot.rare.funcl)) + geom_point()
ggplot(prot.lvl.mutations, aes(x=n.mut.prot, y=n.prot.comm.funcl)) + geom_point()
ggplot(prot.lvl.mutations, aes(x=n.mut.prot, y=n.prot.comm.funcl+n.prot.rare.funcl)) + geom_point()

prot.lm <- lm(n.prot.comm.funcl ~ n.mut.prot, prot.lvl.mutations)
summary(prot.lm) # p.val = 2e-16, R-squared=0.2314 
prot.rare.var <- lm(n.prot.rare.funcl ~ n.mut.prot, prot.lvl.mutations)
summary(prot.rare.var) # p.val = 2e-16, R-squared=0.9571 
prot.all.funcl.var <- lm(n.prot.comm.funcl + n.prot.rare.funcl ~ n.mut.prot, prot.lvl.mutations)
summary(prot.all.funcl.var) # p.val = 2e-16, R-squared=0.9554

prot.lvl.mutations$RVIS.prot <- studres(prot.lm)
domain.mutcount <- merge(domain.mutcount, prot.lvl.mutations[,c(1,6)], by="ENSP", all=TRUE) 
```

## Plot the distribution of protein-level RVIS scores
```{r}
ggplot(prot.lvl.mutations, aes(RVIS.prot)) + geom_histogram()

# define the domains having the bottom 5% RVIS scores as constrained
constrained.prot.RVIS <-
  prot.lvl.mutations[order(prot.lvl.mutations$RVIS.prot),][1:as.integer(0.05*nrow(prot.lvl.mutations)),]
# 347/6,946 of the proteins have at least one constrained domain (5%, defined)

constrained.prot.RVIS$constrained.prot <- TRUE

domain.mutcount <- merge(domain.mutcount,
                         constrained.prot.RVIS[c("ENSP","constrained.prot")],
                         by=c("ENSP"), all=TRUE)

domain.mutcount[is.na(domain.mutcount$constrained.prot),]$constrained.prot <- FALSE

# Plotting regression again with colors
ggplot(domain.mutcount, aes(x=n.mut.prot, y=n.prot.comm.funcl, color=constrained.prot)) +
  geom_point() + 
  geom_smooth(color="black", method="lm", se=FALSE, linetype="solid", fullrange=TRUE) +
  scale_color_manual(values = c("grey", "red"))
```

# Regress domain-level RVIS against protein-level RVIS
```{r}
# subRVIS = bottom 5%
ggplot(domain.mutcount, aes(x=RVIS.prot, y=RVIS.dom, color=constrained.dom)) + 
  geom_point() + 
  geom_smooth(color="black", method="lm", se=FALSE, linetype="solid", fullrange=TRUE) + 
  scale_color_manual(values = c("grey", "red")) + xlim(-3,10)

# subRVIS = bottom 1%
ggplot(domain.mutcount, aes(x=RVIS.prot, y=RVIS.dom, color=constrained.dom2)) + 
  geom_point() + 
  geom_smooth(color="black", method="lm", se=FALSE, linetype="solid", fullrange=TRUE) + 
  scale_color_manual(name=c(), labels=c("domain unconstrained", "domain constrained"), values = c("grey", "red")) + 
  xlim(-3,10) + xlab("Protein Level RVIS") + ylab("Domain Level RVIS") + 
  ggtitle("Comparison between Protein and Domain Level RVIS")
lm(domain.mutcount$RVIS.dom ~ domain.mutcount$RVIS.prot) %>% summary

# protRVIS = bottom 5%
ggplot(domain.mutcount, aes(x=RVIS.prot, y=RVIS.dom, color=constrained.prot)) + 
  geom_point() + 
  geom_smooth(color="black", method="lm", se=FALSE, linetype="solid", fullrange=TRUE) + 
  scale_color_manual(values = c("grey", "red")) + xlim(-3,10)

```

This suggests that proteins that has high mutation count may have domains that are depleted in mutations (i.e. nonessential proteins may have essential domains). That said, according to the current cutoff of 5%, we dont even classified these domain instances as constrained.

Also, we don't observe the converse case (high domain level RVIS, low protein level RVIS), which suggests that a protein might be depleted in mutation, while none of its domains are.  

# Analysis using shuffling method 
```{r}
shuffle <- read.csv("shuffle.csv") # 29,294 unique domains

ggplot(shuffle, aes(shuffle.p.val.dom)) + geom_histogram()
ggplot(shuffle, aes(shuffle.p.val.mut)) + geom_histogram()
qqunif.plot(shuffle$shuffle.p.val.dom + 1e-6)
qqunif.plot(shuffle$shuffle.p.val.mut + 1e-6)


shuffle$p.adj.dom <- p.adjust(shuffle$shuffle.p.val.dom, "BH")
shuffle$p.adj.mut <- p.adjust(shuffle$shuffle.p.val.mut, "BH")

ggplot(shuffle, aes(p.adj.dom)) + geom_histogram()
ggplot(shuffle, aes(p.adj.mut)) + geom_histogram()

constrained.shuffle.dom <- shuffle[shuffle$p.adj.dom < 0.05,] # 1,100/29,294 domains (3.7%)  
constrained.shuffle.mut <- shuffle[shuffle$p.adj.mut < 0.05,] # 495/29,294 domains (1.6%)

```

# Intersection between the three measures 
```{r}
constrained.Fisher$temp <- paste(constrained.Fisher$ENSP,
                                 constrained.Fisher$cluster_membership,
                                 sep = "-")
constrained.dom.RVIS$temp <- paste(constrained.dom.RVIS$ENSP,
                                   constrained.dom.RVIS$cluster_membership,
                                   sep = "-")

# Create template to transform ENSG annotation into ENSP
template = df[,c("ENSP", "ENSG")] %>% unique
template = template[template$ENSG != template$ENSG[1],]
constrained.shuffle.dom = merge(template, constrained.shuffle.dom, by="ENSG")
constrained.shuffle.dom$temp <- paste(constrained.shuffle.dom$ENSP, 
                                      constrained.shuffle.dom$cluster_membership,
                                      sep = "-")

intersect(constrained.Fisher$temp %>% as.character(), 
          constrained.dom.RVIS$temp %>% as.character()) %>% length #42
intersect(constrained.Fisher$temp %>% as.character(), 
          constrained.shuffle.dom$temp %>% as.character()) %>% length # 648
intersect(constrained.shuffle.dom$temp %>% as.character(), 
          constrained.dom.RVIS$temp %>% as.character()) %>% length # 71

intersect(intersect(constrained.Fisher$temp %>% as.character(), 
          constrained.dom.RVIS$temp %>% as.character()), 
          constrained.shuffle.dom$temp %>% as.character()) %>%  length # 24

```


# Validation using ClinVar 
```{r}
# Setup clinvar 
constrained.Fisher # 1,123/36,028
constrained.dom.RVIS # 1,810/36,028
constrained.prot.RVIS # 347/36,028
constrained.shuffle.dom # 1,100/29,294
constrained.shuffle.mut # 495/29,294

clinvar = read.csv("../clinvar_data/clinvar_reduced.csv") #36,208
clinvar = merge(template, clinvar, by="ENSG")
clinvar.p = clinvar[,c("ENSP", "cluster_membership","pathogenic.mut")]

## Merge clinvar with domain mutcount dataset
domain.mutcount <- merge(domain.mutcount, clinvar.p, 
                         by=c("ENSP", "cluster_membership"))

## Merge clinvar with shuffle dataset
shuffle = merge(template, shuffle, by="ENSG")
shuffle = merge(shuffle, clinvar.p, 
                             by=c("ENSP", "cluster_membership"))

shuffle$constrained.dom <- FALSE
shuffle[shuffle$p.adj.dom < 0.05,]$constrained.dom <- TRUE
shuffle$constrained.mut <- FALSE
shuffle[shuffle$p.adj.mut < 0.05,]$constrained.mut <- TRUE

```
```{r}
# Fisher's test
domain.mutcount$pathogenic.mut.norm <- domain.mutcount$pathogenic.mut / domain.mutcount$cluster_size
temp = domain.mutcount[, c("ENSP", "cluster_membership", "cluster_size")]
shuffle = merge(shuffle, temp, by=c("ENSP", "cluster_membership"))
shuffle$pathogenic.mut.norm <- shuffle$pathogenic.mut / shuffle$cluster_size

# Fisher's test
domain.mutcount$fisher.constrained <- FALSE
domain.mutcount[domain.mutcount$Fisher.BH.adj < 0.1 &
                        domain.mutcount$Fisher.odd.ratio<1,]$fisher.constrained <- TRUE
ggplot(domain.mutcount, aes(fisher.constrained, pathogenic.mut.norm)) + geom_boxplot() + ylim(0, 0.1)
ggplot(domain.mutcount, aes(fisher.constrained, pathogenic.mut.norm)) + geom_violin() + 
  ylim(0, 0.1) + scale_x_discrete(name=c(),labels=c("unconstrained", "constrained")) + 
  ylab("Mutation frequency inside the domain (normalised)") + 
  ggtitle("Fisher's Test")

wilcox.test(domain.mutcount[domain.mutcount$fisher.constrained,]$pathogenic.mut.norm,
            domain.mutcount[!domain.mutcount$fisher.constrained,]$pathogenic.mut.norm) #0.2618
kruskal.test(domain.mutcount$pathogenic.mut.norm, domain.mutcount$fisher.constrained) #0.2618
ks.test(domain.mutcount[domain.mutcount$fisher.constrained,]$pathogenic.mut.norm,
            domain.mutcount[!domain.mutcount$fisher.constrained,]$pathogenic.mut.norm, 
        alternative = "l") # 0.9725

# Domain level RVIS
## bottom 5%
ggplot(domain.mutcount, aes(constrained.dom, pathogenic.mut.norm)) + geom_boxplot() + ylim(0, 0.1)
ggplot(domain.mutcount, aes(constrained.dom, pathogenic.mut.norm)) + geom_violin() + 
  ylim(0, 0.1) + scale_x_discrete(name=c(),labels=c("unconstrained", "constrained")) + 
  ylab("Mutation frequency inside the domain (normalised)") + 
  ggtitle("RVIS Method at 5th percentile")

wilcox.test(domain.mutcount[domain.mutcount$constrained.dom,]$pathogenic.mut.norm,
            domain.mutcount[!domain.mutcount$constrained.dom,]$pathogenic.mut.norm) # 2.2e-16
kruskal.test(domain.mutcount$pathogenic.mut.norm, domain.mutcount$constrained.dom) # 2.2e-16
ks.test(domain.mutcount[domain.mutcount$constrained.dom,]$pathogenic.mut.norm,
            domain.mutcount[!domain.mutcount$constrained.dom,]$pathogenic.mut.norm,
        alternative = "l") # 8.294e-10
domain.mutcount

## bottom 1%
ggplot(domain.mutcount, aes(constrained.dom2, pathogenic.mut.norm)) + geom_boxplot() + ylim(0, 0.1)
ggplot(domain.mutcount, aes(constrained.dom2, pathogenic.mut.norm)) + geom_violin() + 
  ylim(0, 0.1) + scale_x_discrete(name=c(),labels=c("unconstrained", "constrained")) + 
  ylab("Mutation frequency inside the domain (normalised)") + 
  ggtitle("RVIS Method at 1st percentile") + coord_cartesian(ylim=c(0, 0.04)) + 
  stat_summary(fun.y = mean, geom="point",colour="darkred", size=3) 

summary(domain.mutcount[domain.mutcount$constrained.dom2,]$pathogenic.mut.norm) #0.4906
summary(domain.mutcount[!domain.mutcount$constrained.dom2,]$pathogenic.mut.norm) #0.4771

  
ggplot(domain.mutcount[domain.mutcount$constrained.dom2,], aes(x=pathogenic.mut.norm)) + geom_histogram()
ggplot(domain.mutcount[!domain.mutcount$constrained.dom2,], aes(x=pathogenic.mut.norm)) + geom_histogram()

hist(domain.mutcount[domain.mutcount$pathogenic.mut.norm &
                      domain.mutcount$pathogenic.mut.norm >= 0,]$pathogenic.mut.norm, breaks = 20)

hist(domain.mutcount[!(domain.mutcount$constrained.dom2) &
                      domain.mutcount$pathogenic.mut.norm >= 0,]$pathogenic.mut.norm, breaks = 20)

wilcox.test(domain.mutcount[domain.mutcount$constrained.dom2,]$pathogenic.mut.norm,
            domain.mutcount[!domain.mutcount$constrained.dom2,]$pathogenic.mut.norm) # 9.319e-11
kruskal.test(domain.mutcount$pathogenic.mut.norm, domain.mutcount$constrained.dom) # 2.2e-16
ks.test(domain.mutcount[domain.mutcount$constrained.dom2,]$pathogenic.mut.norm,
            domain.mutcount[!domain.mutcount$constrained.dom2,]$pathogenic.mut.norm, 
        alternative = "l") #  0.000912


# Shuffling test
## Shuffle the domain annotation of the residue 
ggplot(shuffle, aes(constrained.dom, pathogenic.mut.norm)) + geom_boxplot()+ ylim(0, 0.1)
ggplot(shuffle, aes(constrained.dom, pathogenic.mut.norm)) + geom_violin() + 
  ylim(0, 0.1) + scale_x_discrete(name=c(),labels=c("unconstrained", "constrained")) + 
  ylab("Mutation frequency inside the domain (normalised)") + 
  ggtitle("Shuffle Method")

wilcox.test(shuffle[shuffle$constrained.dom,]$pathogenic.mut.norm
            , shuffle[!shuffle$constrained.dom,]$pathogenic.mut.norm) # 0.9164
kruskal.test(shuffle$pathogenic.mut.norm, shuffle$constrained.dom) # 0.9164
ks.test(shuffle[shuffle$constrained.dom,]$pathogenic.mut.norm
            , shuffle[!shuffle$constrained.dom,]$pathogenic.mut.norm, 
        alternative="l") #  0.9635

## Shuffle the mutations 
ggplot(shuffle, aes(constrained.mut, pathogenic.mut.norm)) + geom_boxplot() + ylim(0, 0.1)
ggplot(shuffle, aes(constrained.mut, pathogenic.mut.norm)) + geom_violin() + 
  ylim(0, 0.1) + scale_x_discrete(name=c(),labels=c("unconstrained", "constrained")) + 
  ylab("Mutation frequency inside the domain (normalised)") + 
  ggtitle("Shuffle Method (mutations)")

wilcox.test(shuffle[shuffle$constrained.mut,]$pathogenic.mut.norm
            , shuffle[!shuffle$constrained.mut,]$pathogenic.mut.norm) # 0.3447
kruskal.test(shuffle$pathogenic.mut.norm, shuffle$constrained.mut) # 0.3447
ks.test(shuffle[shuffle$constrained.mut,]$pathogenic.mut.norm
            , shuffle[!shuffle$constrained.mut,]$pathogenic.mut.norm, 
        alternative="l") #  0.8244

```

- For the shuffling method, what is the difference between dom and mut, how come the results is vastly different?
- Why is it important to plot p-value histogram? What does it mean to have peak at both ends?
- Does BH correction requires the p-value distribution to already peak at one side?  
- Read more on mid-p value correction
- Is it possible to argue that the RVIS pattern we are seeing now is biased because of how our samples are biased towards the shorter clusters? 


Analysis of GO annotations 
```{r}
library(clusterProfiler)
library(EnsDb.Hsapiens.v75)
library(org.Hs.eg.db)
domain.mutcount <- merge(domain.mutcount, template, by="ENSP")

gene.GO = domain.mutcount[domain.mutcount$constrained.dom2,]$ENSG %>% as.character %>% unique
univ.GO = domain.mutcount$ENSG %>% as.character %>% unique
length(univ.GO)
ego <- enrichGO(gene = gene.GO, universe= univ.GO, OrgDb=org.Hs.eg.db, keyType= 'ENSEMBL', ont = "ALL", pAdjustMethod = "BH", pvalueCutoff  = 0.1, qvalueCutoff  = 0.1, readable= TRUE)
ego
dotplot(ego, showCategory=5)
emapplot(ego)
```

## Extra plots of the size distributions
```{r}
ggplot(domain.mutcount, aes(prot.size)) + geom_histogram() + xlab("Protein Length") + 
  ggtitle("Distribution of protein lengths")
domain.mutcount$prot.size %>% summary
ggplot(domain.mutcount, aes(cluster_size)) + geom_histogram() + xlab("Domain Length") + 
  ggtitle("Distribution of domain lengths")
domain.mutcount$cluster_size %>% summary
```


```{r}
sessionInfo()
```
